First steps towards a formalization of Forcing

### 2018-06-24 LSFA/isabelle-zf.tex
nueva versión del párrafo de locales

>>>>

Mathematical texts usually start by fixing the context which defines
parameters and assumptions necessary to develop theorems
and results. In Isabelle the way of defining contexts is through
\emph{locales}~\cite{ballarin2010tutorial}.
Locales can be combined and extended adding more parameters and assuming
more facts, leading to a new locale. For example a context describing
lattices can be extended to distributive lattices.
The way to instantiate a locale is \emph{interpreting} it, which consists
of giving concrete values to parameters and proving the assumptions.
In our work, we use locales to organize the formalization and to make
explicit the assumptions of the most important results.
